Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1) \note{\scriptsize Authors, please add/check middle initials and affiliations}

### 2014-04-12 WSSSPE1_report/WSSSPE1_summary_report.tex
Adding prose about resources listed.

The literature below, suggested by attendees, addresses both non-scientific
software projects, as well as scientific projects.  The selections address both
descriptive and prescriptive approaches to communities. 
\begin{itemize}
\item \cite{howison_scientific_2011, howison_incentives_2013}
\item \cite{citeulike:11831265}
\item \cite{citeulike:7888211}
\item \cite{citeulike:478633}
\item \cite{opac-b1134063}
\item \cite{Trapani:2011}
\item \cite{Allsopp:2012}
\item \cite{1749-4699-6-1-015010}
\item \cite{Turk:2013:SCH:2484762.2484782}
\end{itemize}

>>>>

The literature below, suggested by attendees, addresses both non-scientific
software projects, as well as scientific projects.  The selections address both
descriptive and prescriptive approaches to communities.

Both \cite{howison_scientific_2011} and \cite{howison_incentives_2013} 
study how scientific software collectives self-organize and address issues of
incentive, long-term support, and development of infrastructure as well as new
features.  As noted elsewhere in this summary,
\cite{Turk:2013:SCH:2484762.2484782} shared prescriptions from two software
communities in astrophysics.

From the perspective of developing prescriptions for successful scientific
software development, both \cite{citeulike:11831265} and
\cite{1749-4699-6-1-015010} share experiences and suggestions for developing
sustainable practices.  \cite{citeulike:11831265} proposes "ten simple rules"
for developing open source scientific software, focusing on both the choices
made during development and the sustainability of practices in the long term.  
\cite{1749-4699-6-1-015010} describes the development and long-term growth of
the \texttt{deal.II} library, and how its place in its ecosystem of libraries,
applications and domains has shaped its development and community trajectory.

From more traditional open source development, resources were shared that
developed communities explicitly, such as 
\cite{citeulike:7888211} and \cite{Trapani:2011}, focusing on
large-scale projects such as the Ubuntu linux distribution and smaller-scale
volunteer-developed projects like such as ThinkUp, respectively.
The process of open source development, while less explicitly focused on
community building, outlined in \cite{citeulike:478633} was seen as a valuable
resource, particularly when combined with the management and personal
interaction techniques outlined in \cite{opac-b1134063}.  Growing diversity in
communities was directly addressed in \cite{Allsopp:2012}, where experiences
growing the diversity of technical conferences in open source were described.
